Embodied Neuromorphic Benchmarks

### 2015-08-13 paper/paper.tex
clarified minsim worseness
calrifications

\subsection{Cheap Robotics for Adaptive Control}

@@

Now that we have this physical example of the task out minimal simulation
benchmark is meant to cover, we can use it to calibrate the parameters of
the simulation.  For example, communication with the EV3 happens around
200Hz, meaning that there must be a delay on the order of 0.005 seconds.  Given
this, we set the delays in the simulation to be uniformly chosen between
0 and 0.01.  Importantly, we do not need to exactly measure the delay in the
EV3 robot --- we just make sure that the minimal simulation is worse.

For sensor noise, we note that the EV3 rotation encoders for the motors (the
devices that measure $q$) have a resolution of 0.0175 (1 degree).  This is a
very different sort of noise than the gaussian noise used in the simulation,
so we set the simulation noise to be much larger (uniformly distributed
between 0 and 0.1).  Similarly, the motor resolution is 0.01, as it accepts 
integer values up to 100, so we set the motor noise to be uniform between
0 and 0.1.

>>>>

\subsection{Calibrating the Minimal Simulation via Cheap Robotics}

@@

Now that we have this physical example of the task out minimal simulation
benchmark is meant to cover, we can use it to calibrate the parameters of
the simulation.  For example, communication with the EV3 happens around
200Hz, meaning that there must be a delay on the order of 0.005 seconds.  Given
this, we set the delays in the simulation to be uniformly chosen between
0 and 0.01.  Importantly, we do not need to exactly measure the delay in the
EV3 robot --- we just make sure that the minimal simulation covers even worse
cases.

For sensor noise, we note that the EV3 rotation encoders for the motors (the
devices that measure $q$) have a resolution of 0.0175 (1 degree).  This is a
very different sort of noise than the gaussian noise used in the simulation,
so we set the simulation noise $\sigma_q$ to be much larger (uniformly distributed
between 0 and 0.1).  Similarly, the motor resolution is 0.01, as it accepts 
integer values up to 100, so we set the motor noise $\sigma_u$ to be uniform between
0 and 0.1.
